|

### 2025-12-01 manuscript/pre_print.qmd
JS and HC COIs/Financial disclosures

>>>>

# Financial Disclosures/Conflicts of Interest
Hannah Cabré was supported by the National Institute of Diabetes and Digestive and Kidney Diseases of the National Institutes of Health under Award Number T32DK064584. James Steele provides research consultancy through his company Steele Research Limited, is contracted currently by MacroFactor and Kieser Australia through Steele Research Limited, and has also received travel expenses and honoraria for speaking from fit20 International, Exercise School Portugal, and Discover Strength.

The content is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health or any other funding agencies or institutions noted above.

### 2025-12-01 manuscript/pre_print.tex
JS and HC COIs/Financial disclosures

>>>>

\section{Financial Disclosures/Conflicts of
Interest}\label{financial-disclosuresconflicts-of-interest}

Hannah Cabré was supported by the National Institute of Diabetes and
Digestive and Kidney Diseases of the National Institutes of Health under
Award Number T32DK064584. James Steele provides research consultancy
through his company Steele Research Limited, is contracted currently by
MacroFactor and Kieser Australia through Steele Research Limited, and
has also received travel expenses and honoraria for speaking from fit20
International, Exercise School Portugal, and Discover Strength.

The content is solely the responsibility of the authors and does not
necessarily represent the official views of the National Institutes of
Health or any other funding agencies or institutions noted above.
